Fractional Types

### 2019-11-20 fracGC/p.tex
better picture more explanations

\usepackage{booktabs}  
\usepackage{subcaption} 
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{bbm}
\usepackage[greek,english]{babel}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{autofe}
\usepackage[references]{agda} 
\usepackage{newunicodechar}
\usepackage[nocenter]{qtree}
\usepackage{multicol}  
\usepackage{tikz}
\usepackage{bbold}
\usetikzlibrary{cd}
\usetikzlibrary{quotes}

@@

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,scale=0.8, yscale=-1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
%Straight Lines [id:da05403550183378514] 
\draw    (10,20) -- (190,20) ;
%Shape: Circle [id:dp8701819096818126] 
\draw   (138.75,21.25) .. controls (138.75,15.04) and (143.79,10) .. (150,10) .. controls (156.21,10) and (161.25,15.04) .. (161.25,21.25) .. controls (161.25,27.46) and (156.21,32.5) .. (150,32.5) .. controls (143.79,32.5) and (138.75,27.46) .. (138.75,21.25) -- cycle ;
%Straight Lines [id:da3470499764023487] 
\draw    (150,80) -- (150,10) ;
%Straight Lines [id:da9303973632982276] 
\draw    (40,80) -- (190,80) ;
%Shape: Circle [id:dp03942567054970991] 
\draw   (48.75,81.33) .. controls (48.75,75.12) and (53.79,70.08) .. (60,70.08) .. controls (66.21,70.08) and (71.25,75.12) .. (71.25,81.33) .. controls (71.25,87.55) and (66.21,92.58) .. (60,92.58) .. controls (53.79,92.58) and (48.75,87.55) .. (48.75,81.33) -- cycle ;
%Straight Lines [id:da08295302434157614] 
\draw    (60,92.58) -- (60,20) ;
%Shape: Arc [id:dp2904677718814479] 
\draw  [draw opacity=0] (38.49,110.13) .. controls (28.3,109.22) and (20.27,102.7) .. (20.15,94.89) .. controls (20.02,86.57) and (28.89,79.93) .. (40,80) -- (40.38,95.12) -- cycle ; \draw   (38.49,110.13) .. controls (28.3,109.22) and (20.27,102.7) .. (20.15,94.89) .. controls (20.02,86.57) and (28.89,79.93) .. (40,80) ;
%Straight Lines [id:da32172184710713914] 
\draw    (38.49,110.13) -- (250,110) ;
%Shape: Arc [id:dp8398868072937593] 
\draw  [draw opacity=0] (248.77,109.75) .. controls (262.77,109.82) and (274.32,103.33) .. (274.64,95.17) .. controls (274.95,87.02) and (263.95,80.28) .. (250,80) -- (249.05,94.87) -- cycle ; \draw   (248.77,109.75) .. controls (262.77,109.82) and (274.32,103.33) .. (274.64,95.17) .. controls (274.95,87.02) and (263.95,80.28) .. (250,80) ;
%Straight Lines [id:da5220296307776525] 
\draw    (190,20) -- (250,80) ;
%Straight Lines [id:da320377013704656] 
\draw    (190,80) -- (250,20) ;
%Straight Lines [id:da8933694171914682] 
\draw    (250,20) -- (308,20) ;
\end{tikzpicture}

>>>>

\usepackage{booktabs}  
\usepackage{subcaption} 
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{bbm}
\usepackage[greek,english]{babel}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{autofe}
\usepackage[references]{agda} 
\usepackage{newunicodechar}
\usepackage[nocenter]{qtree}
\usepackage{multicol}  
\usepackage{bbold}
\usepackage{tikz}
\usetikzlibrary{cd}
\usetikzlibrary{quotes}

\usepackage{tikzit}
\input{frac.tikzstyles}

@@

The first example below illustrates the basic functionality of
ancillae. The circuit has one input and one output. Immediately after
receiving the input, the circuit generates an ancilla wire and its
corresponding gc process (first line in the Agda definition). The
original input and the ancilla wire interact using two
\AgdaFunction{CNOT} gates, after which the ancilla wire is redirected
to the output (second line in the Agda code). Finally the original
input is gc'ed (third line in the Agda code). The entire circuit is
extensionally equivalent to the identity function.

\begin{center}
\input{idpic.tikz}
\end{center}
